Functional vs. Object Oriented Programming

### 2015-10-06 article.tex
Hypothesis draft added.

\section{Methods}
\section{Results and Analysis}

>>>>

Human resources and time consumption are very important factors in software development, especially for companies that want to optimise profits and gain advantages from the market.

We strongly believe that, using functional programming languages, developers will be more productive and they will also produce higher quality code that will allow them to reuse much of it when releasing newer versions of their programs.

\section{Methods}

A quantitative method is used for this project because the authors will gather data from many sources and they will report in the paper. Afterward, the analysis of the gathered data will be performed so that the initial hypothesis will be either accepted or rejected.

The approach used will be deductive because we started this research with our own hypothesis on the basis of existing theories, for instance, regarding the benefits of FP and the advantages that developers can gain in software production.

Afterward, when the data will be acquired, the authors will perform observation and analysis of the gotten results. From that, it will be possible to accept or reject the initial hypothesis.

\section{Results and Analysis}
